AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-14 publications/iaai21/dora_outlier_detection_iaai.tex
Add precision-at-k results for planetary rover. (#60,#42)
Add selection figure for planetary rover results. (#60,#42)

\begin{table}
  \caption{Precision at $N=n_{outlier}$ for Earth science dataset. }
  \label{tab:faw_results}
  \centering
  \begin{tabular}{cc}
    \hline
    Algorithm & Precision at $N=n_{outlier}$ \\
    \hline
    Random & 0.32 \\
    DEMUD & 0.41 \\
    PCA & 0.41 \\
    PAE & 0.41 \\
    RX & 0.43 \\
    Isolation Forest & 0.46 \\
    \textbf{Negative Sampling} & \textbf{0.49} \\
    \hline
  \end{tabular}
\end{table}

@@

>>>>

\begin{table}
  \caption{Precision at $N=n_{outlier}$ for three applications; the
  best result for each data set is in bold.}
  \label{tab:faw_results}
  \centering
  \begin{tabular}{l|ccc}
    \hline
    Algorithm & Earth & Planetary & Astrophysics \\
    \hline
    PCA               & 0.41 & 0.44 \\
    DEMUD             & 0.41 & 0.44 \\
    \hline
    RX                & 0.43 & ---- \\
    LRX               & ---- & 0.33 \\
    \hline
    Isolation Forest  & 0.46 & \textbf{0.56} \\
    \hline
    PAE               & 0.41 & 0.22 \\
    Neg. Sampling & \textbf{0.49} & 0.33 \\
    \hline
    Random            & 0.32 & 0.11 \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/planetary_combined_plot.pdf}
    \caption{Number of true outliers ranked in top $N$ selections for 
    planetary rover dataset.}
    \label{fig:planetary_results}
\end{figure}
